---
title: "Data gathering and cleaning - GBIF & Species Link"
author: "JuliaNiemeyer"
date: "28/04/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```
install.packages("rgbif")
install.packages("Taxonstand")
install.packages("CoordinateCleaner")
install.packages("maps")
install.packages("dplyr")
install.packages("devtools")
```
``` {if needed install the rocc package:}
devtools::install_github("saramortara/rocc", force = TRUE)
```


``` {r loading pkg}
library(rgbif)
library(Taxonstand)
library(CoordinateCleaner)
library(maps)
library(dplyr)
library(devtools)
library(rocc)
```

Read the spreadsheet with the names of all your species (should be located in the "data" folder).

``` {read table and vector with species names}
Sptable <- read.csv("./data/Species_ex.csv")
scientificName <- as.vector(Sptable$Species)

```
To do a trial before running the whole dataset, I will run only for species 4

``` {for a trial}
  a = 4

```

##I disabled the for so I can run it only for a=4  
for (a in 1:length(scientificName)) {

Get records from SpeciesLink and save ir to the "results" directory (the creation of the results directory is part of the rspeciesLink function)
   
```{run the entire script}
rspeciesLink(filename = paste0("raw_data_SpeciesLink_",scientificName[a]), scientificName = scientificName[a], Coordinates = "Yes")
    
#read the above table as csv to work on it
file_path <- file.path("./results", paste0("raw_data_SpeciesLink_",scientificName[a], ".csv"))
spLink <- read.csv(file_path)
#View(spLink)
    
#Get occurence points from GBIF
gbif_input <- occ_search(scientificName = scientificName[a],
                             return = "data")
    
#Save it as a csv file
file_path2 <- file.path("./results", paste0("raw_data_GBIF_",scientificName[a], ".csv"))
write.csv(gbif_input, file_path2, row.names = FALSE)
gbif <- read.csv(file_path2)
#View(gbif)
    
# 2. Checking species taxonomy
#Let's check the unique entries for the species name we just searched.
    
########TAXONOMIC CLEANING
  
##Check status_function by Sara Mortara 

```


